Motivation

### 2017-07-19 Reports/USAID.tex
pobonita

\begin{figure}[H]
    \caption{Duration predictions}
    \label{duration_predictions}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_caducidad.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_convenio.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_pierde.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_gana.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_desiste.tiff}
     \end{subfigure}
        \end{center}
        %{\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
\end{figure}

\begin{figure}[H]
    \caption{Compensation predictions}
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_convenio.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_laudo_gana.tiff}
     \end{subfigure}
  \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}

@@

\begin{figure}[H]
\centering
\caption{Calculator predictions in the first pilot}
\includegraphics{calctreat.png}
\end{figure}

@@

The final models were chosen based on the Mean Squared Error, and
certain aspects of the out-of-sample error distributions. For this
second criterion we estimated this distribution by retraining the model
1000 times on a 70-30 train-test split and computing prediction errors. Figure \ref{continuous_predictions}

\begin{figure}[H]
    \caption{Compensation predictions}
    \label{continuous_predictions}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{prediction_convenio.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{prediction_laudo.tiff}
     \end{subfigure}
  \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}

>>>>

\begin{figure}[H]
    \caption{Duration predictions in the first pilot}
    \label{duration_predictions}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_caducidad.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_convenio.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_pierde.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_laudo_gana.tiff}
     \end{subfigure}
     \hfill
         \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_duracion_desiste.tiff}
     \end{subfigure}
        \end{center}
        %{\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
\end{figure}

\begin{figure}[H]
    \caption{Compensation predictions in the first pilot}
    \label{}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_convenio.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{mod_liqtotal_laudo_gana.tiff}
     \end{subfigure}
  \end{center}
        {\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
        {\footnotesize \textit{R Script: } \texttt{}}
\end{figure}

@@

\begin{figure}[H]
\centering
\caption{Information sheet in the first pilot (shown to both parties)}
\includegraphics{calctreat.png}
\end{figure}

@@

The final models were chosen based on the Mean Squared Error, and
certain aspects of the out-of-sample error distributions. For this
second criterion we estimated this distribution by retraining the model
1000 times on a 70-30 train-test split and computing prediction errors. Figure \ref{continuous_predictions} shows the out-of-sample fit for our continuous models. For each model, we regress the prediction on our dependent variable and show the $R^2$ in the plot subtitle.

\begin{figure}[H]
    \caption{Compensation predictions in the second pilot}
    \label{continuous_predictions}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{prediction_convenio.tiff}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
    \centering
        \includegraphics[width=.75\textwidth]{prediction_laudo.tiff}
     \end{subfigure}
  \end{center}
        %{\footnotesize \textit{Notes: } Scatter plot of compensation predictions and outcomes }
\end{figure}
